### 2020-01-13 paper/conclusion.tex

Five different absorbing materials are considered based on their neutronics and 
safety performance: B$_4$C-90 (boron is enriched to 90\% $^{10}$B), HfB$_2$, 
HfH$_{1.62}$, Eu$_2$O$_3$, and Gd$_2$O$_3$. Enriched B$_4$C-90 has the largest 
absorption ability, while Gd$_2$O$_3$ has the lowest absorption compared with 
the other absorbing materials in this study. Both CSD and SSD clusters are 
separately able to shut down the reactor initially loaded with $^{233}$U and 
reactor-grade Pu regardless of the absorbing material type. However, only SSD 
clusters made of B$_4$C-90 are able to shut down the SD-TMSR initially loaded 
with transuranium vector from \gls{LWR}. The reason for this is much larger 
absorption cross section of $^{10}$B in the relatively soft neutron energy 
spectrum of the SD-TMSR core started with TRU.

In case of malfunction of the other CR clusters (e.g., stuck in the upper 
position), the outer ring of the CSD failures to counteract the excess 
reactivity of the core initially loaded with reactor-grade Pu and transuranic 
(TRU) elements. However, the worth of the outer ring of the CSD is sufficient 
to compensate the excess reactivity for the core refueled by $^{233}$U.

@@

\section{Future work}
In Part II of this research effort we will evaluate effect of fuel salt 
burnup on the CRW. The depleted fuel composition will be obtained using 
SERPENT-2 online reprocessing subroutine \cite{aufiero2013extended} and 
batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018, 
rykhlevskii_milestone_2019}. Additionally, the authors intend to investigate 
kinetic parameters (effective delayed neutron fraction $\beta_{eff}$ and 
effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 
during the SD-TMSR operation. These parameters are crucial for accident 
transient analysis, which will be performed using Moltres 
\cite{lindsay_introduction_2018}, multi-physics code for liquid-fueled MSR 
simulation with taking into account the neutron precursors drift.

>>>>

Five different absorbing materials are considered based on their neutronics and 
safety performance: B$_4$C-90 (boron is enriched to 90\% $^{10}$B), HfB$_2$, 
HfH$_{1.62}$, Eu$_2$O$_3$, and Gd$_2$O$_3$. Enriched B$_4$C-90 has the largest 
absorption ability, while Gd$_2$O$_3$ has the lowest absorption compared with 
the other absorbing materials in this study. Both CSD and SSD clusters are 
separately able to shut down the reactor initially loaded with $^{233}$U and 
reactor-grade Pu regardless of the absorbing material type. However, only SSD 
clusters made of B$_4$C-90 are able to shut down the SD-TMSR initially loaded 
with transuranic vector from \gls{LWR}. The reason for this is much larger 
absorption cross section of $^{10}$B in the relatively soft neutron energy 
spectrum of the SD-TMSR core started with TRU.

In case of malfunction of the other CR clusters (e.g., stuck in the upper 
position), the outer ring of the CSD failed to counteract the excess 
reactivity of the core initially loaded with reactor-grade Pu and transuranic 
(TRU) elements. However, the worth of the outer ring of the CSD is sufficient 
to compensate the excess reactivity for the core refueled by $^{233}$U.

@@

\section{Future work}
In Part II of this research effort, we will evaluate effect of fuel salt 
burnup on the CRW. The depleted fuel composition will be obtained using 
SERPENT-2 online reprocessing subroutine \cite{aufiero2013extended} and 
batch-wise tool SaltProc \cite{rykhlevskii_arfc/saltproc_2018, 
rykhlevskii_milestone_2019}. Additionally, the authors intend to investigate 
kinetic parameters (effective delayed neutron fraction $\beta_{eff}$ and 
effective delayed neutron precursor decay constant $\lambda_{eff}$) evolution 
during the SD-TMSR operation. These parameters are crucial for accident 
transient analysis, which will be performed using Moltres 
\cite{lindsay_introduction_2018}, multi-physics code for liquid-fueled MSR 
simulation with taking into account the neutron precursors drift.

### 2020-01-13 paper/methods.tex

The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) design was proposed by the Chinese Academy of Sciences in 2011 
\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
\gls{SD-TMSR} is a graphite-moderated molten salt reactor with a thermal power 
of 2,250 MW$_{th}$. The design of the \gls{SD-TMSR} is inspired by the 
\gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} 
\cite{nuttin2005potential} after modifying the geometry to control the 
positive moderator temperature coefficient in the MSBR. The \gls{SD-TMSR} core 
geometry was described in detail by Li \emph{et al.} and Ashraf \emph{et al.}
\cite{li_optimization_2018,ashraf2020whole}. The core of the 
\gls{SD-TMSR} is a right cylinder divided into the inner zone (486 fuel tubes) 
and the outer zone (522 fuel tubes) to enhance breeding performance.

@@

Since the total quantity and distribution of the control assemblies in the SD-TMSR are unknown, we proposed an original distribution as a starting point of this analysis. We added clusters consist of four control rods to specific graphite hexagonal prisms (elements) in the SD-TMSR core. Every four control rods (cluster) can move together as one group. Figure~\ref{fig:graphite_elemen} and~\ref{fig:graphite_elemen1} demonstrate the plan and axial view of the graphite element with the control rods. The total numbers of graphite elements with control rods are 25: 16 CSD and 9 SSD.
\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in} 
	\includegraphics[width=\textwidth]{cr.png}
	\caption{Cross section of the B$_4$C control rod.}
	\label{fig:cr}
\end{figure}
\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{graphite_element.png}
	\caption{$XY$ section of graphite element with the four control rods 
	(cluster) located at the same distance from the fuel channel.}
	\label{fig:graphite_elemen}
\end{figure}
\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{graphite_element1.png}
	\caption{$XZ$ section of graphite element with control rods.}
	\label{fig:graphite_elemen1}
\end{figure}

Figure~\ref{fig:core_25} illustrates the numbering scheme of control rods 
clusters in the SD-TMSR core.
The CSD1-16 clusters are represented as yellow color and distributed as two rings: inner and outer ring (peripheral ring). The inner ring includes CSD from 1 to 6, while the outer ring includes CSD from 7 to 16. Red color stands for SSD1-9 clusters.
We distributed the graphite elements with control rods clusters uniformly in 
the inner core of the SD-TMSR, where the moderator-to-fuel ratio is high.
The selected core segment at the upper left corner of the 
Figure~\ref{fig:core_25} shows that both CSD and SSD clusters consist of four 
control rods located at the same distance from the fuel channel center.
\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{core_25.png}
	\caption{Distribution of the graphite elements with control rods in the SD-TMSR core. Green - fuel salt, blue - graphite, pink - B$_4$C, and light-green - vessel (H-alloy).}
	\label{fig:core_25}
\end{figure}

@@

Interference between control rods (CRs) or shadowing effects occurs when one 
(or more) control rod affects the reactivity worth of another control rod in 
the surroundings. Thus, anti-shadowing is observed when the combined rod worth 
is greater than the sum of the individual worths. Oppositely, the shadowing 
effect appears when the combined rod worth is less than the sum of the 
individual worths. The core height-to-diameter ratio (H/D) and the 
three-dimensional configuration of the control rods affect the degree of the 
interference between CRs \cite{girardin2007control}.

@@

The integral CRW is the total reactivity change due to the control rod full 
insertion or withdrawal. In contrast, the differential CRW is the amount of 
reactivity inserted per unit of withdrawal [\$/cm]. To calculate those 
parameters, we varied the position of CRs clusters from fully withdrawn to 
fully inserted. Equation~\ref{Equ:4} is used to calculate the integral CRW 
[\$], where $k_{i}$ and $k_{i-1}$ are the effective multiplication factor 
after and before CR insertion to i$^{th}$ step. $\beta_{i}$ is the effective 
fraction of delayed neutrons at i$^{th}$ step. N is the number of steps.

>>>>

The Chinese Academy of Sciences proposed the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) design in 2011
\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
\gls{SD-TMSR} is a graphite-moderated molten salt reactor with a thermal power 
of 2,250 MW$_{th}$. The design of the \gls{SD-TMSR} is inspired by the 
\gls{MSBR} \cite{robertson_conceptual_1971} and the \gls{TMSR} 
\cite{nuttin2005potential} after modifying the geometry to control the 
positive moderator temperature coefficient in the MSBR. Li \emph{et al.} and Ashraf \emph{et al.}
described in detail the \gls{SD-TMSR} core geometry
\cite{li_optimization_2018,ashraf2020whole}. The core of the 
\gls{SD-TMSR} is a right cylinder divided into the inner zone (486 fuel tubes) 
and the outer zone (522 fuel tubes) to enhance breeding performance.

@@

Since the total number and distribution of the control assemblies in the SD-TMSR are unknown, we proposed an original distribution as a starting point of this analysis. We added clusters consist of four control rods to specific graphite hexagonal prisms (elements) in the SD-TMSR core. Every four control rods (cluster) can move together as one group. Figure~\ref{fig:graphite_elemen} and~\ref{fig:graphite_elemen1} demonstrate the plan and axial view of the graphite element with the control rods. The total number of graphite elements with control rods are 25: 16 CSD and 9 SSD.
\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in} 
	\includegraphics[width=\textwidth]{cr.png}
	\caption{Cross section of the B$_4$C control rod.}
	\label{fig:cr}
\end{figure}
\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{graphite_element.png}
	\caption{$XY$ section of graphite element with the four control rods 
	(cluster) located at the same distance from the fuel channel.}
	\label{fig:graphite_elemen}
\end{figure}
\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{graphite_element1.png}
	\caption{$XZ$ section of graphite element with control rods.}
	\label{fig:graphite_elemen1}
\end{figure}

Figure~\ref{fig:core_25} illustrates the numbering scheme of control rods 
clusters in the SD-TMSR core.
The CSD1-16 clusters are represented as yellow color and distributed as two rings: inner and outer ring (peripheral ring). The inner ring includes CSD from 1 to 6, while the outer ring includes CSD from 7 to 16. Red color stands for SSD1-9 clusters.
We distributed the graphite elements with control rods clusters uniformly in 
the inner core of the SD-TMSR, in which the moderator-to-fuel ratio is high.
The selected core segment at the upper left corner of the 
Figure~\ref{fig:core_25} shows that both CSD and SSD clusters consist of four 
control rods located at the same distance from the fuel channel center.
\begin{figure}[t!]  % replace 't' with 'b' to \centering
	\centering
	\hspace{+0.65in}
	\includegraphics[width=\textwidth]{core_25.png}
	\caption{Distribution of the graphite elements with control rods in the SD-TMSR core. Green - fuel salt, blue - graphite, pink - B$_4$C, and light-green - vessel (H-alloy).}
	\label{fig:core_25}
\end{figure}

@@

Interference between control rods (CRs) or shadowing effects occur when one 
(or more) control rod affects the reactivity worth of another control rod in 
the surroundings. Thus, the shadowing effect appears when the combined rod worth
is less than the sum of the individual worths. Oppositely, anti-shadowing is observed 
when the combined rod worth is greater than the sum of the individual worths.
The core height-to-diameter ratio (H/D) and the three-dimensional configuration 
of the control rods affect the degree of the interference between CRs \cite{girardin2007control}.

@@

The integral CRW is the total reactivity change due to the control rod full 
insertion or withdrawal. However, the differential CRW is the amount of 
reactivity inserted per unit of withdrawal [\$/cm]. To calculate those 
parameters, we varied the position of CRs clusters from fully withdrawn to 
fully inserted. Equation~\ref{Equ:4} is used to calculate the integral CRW 
[\$], where $k_{i}$ and $k_{i-1}$ are the effective multiplication factor 
after and before CR insertion to i$^{th}$ step. $\beta_{i}$ is the effective 
fraction of delayed neutrons at i$^{th}$ step. $N$ is the number of steps.
